Formalisation of Session-based Lambda Calculus Type Systems

### 2014-11-05 proposal/proposal.tex
A structure developing.

briefly explain the context of the project problem

@@

it is thus clear that the need for
construct an argument for the use of a proof assistant and interactive theorem
proving technologies to formalise a framework for developing type systems
involving session types that are based on lambda calculi so that we can use
such a development to reason about a variety of type systems while minimising
proof effort tie this into an introduction into the subfield of session types
and what they are good for essentially motivating our project in this space
additionally we can introduce the reader to the discipline of interactive
theorem proving and formal methods more generally as a way to formalise
programming languages highlighting the benefits of reusability increased
correctness and something what else could we say i think it would appropriate
to mention that the session types studied so far include both pi and lambda
calculi and it may be beneficil if the reader was informed also the pi
calculus paradigms do not fit well into the existing mainstream programming
language paradigms this seems like it should be in the statement of the problem section down below also i should read more of jtod's slides because this writing just keep writing malarky might just be what i need to pound out the pages because it eliminates thoughts as they come into the head what else adopt and focus we have in the problem statement but perhaps those paragraphs should be re-jigged for up here multithreaded functional programming with linear typing for session types a number of these systems use different type systems but they are based on all the lambda calculus fundamentally so to have a generic framework to encode these variants would save on proof engineering effort as is championed by the POPLMARK challenge aimed at reducing the effort for researchers to code programming language metatheory it provides a library needed to perform various things define various parts of programming languages viewed to be difficult to formalise including handling binders and freshness they also mention handling of linear typing but renege on actually formulating this as part of their challenge they insist it is a future work here is the future

\subsection{A subsection}
Please note your proposal need not follow the included section headings - this
is only a suggested structure. Also add subsections etc as required

>>>>

Two aspects of programming language research are relevant for the problem. The first is concerned with static type systems for ensuring runtime safety properties for concurrent communication systems. The second is the increasing use of proof assistants and interactive theorem provers, for studying and mechanically verifying the semantics and properties of programming languages.

\subsection{On Communication}

@@

\subsection{On Verification}

construct an argument for the use of a proof assistant and interactive theorem proving technologies to formalise a framework for developing type systems involving session types that are based on lambda calculi so that we can use such a development to reason about a variety of type systems while minimising proof effort tie this into an introduction into the subfield of session types and what they are good for essentially motivating our project in this space additionally we can introduce the reader to the discipline of interactivetheorem proving and formal methods more generally as a way to formalise programming languages highlighting the benefits of reusability increased

correctness and something what else could we say i think it would appropriate
to mention that the session types studied so far include both pi and lambda
calculi and it may be beneficil if the reader was informed also the pi
calculus paradigms do not fit well into the existing mainstream programming
language paradigms this seems like it should be in the statement of the problem section down below also i should read more of jtod's slides because this writing just keep writing malarky might just be what i need to pound out the pages because it eliminates thoughts as they come into the head what else adopt and focus we have in the problem statement but perhaps those paragraphs should be re-jigged for up here multithreaded functional programming with linear typing for session types a number of these systems use different type systems but they are based on all the lambda calculus fundamentally so to have a generic framework to encode these variants would save on proof engineering effort as is championed by the POPLMARK challenge aimed at reducing the effort for researchers to code programming language metatheory it provides a library needed to perform various things define various parts of programming languages viewed to be difficult to formalise including handling binders and freshness they also mention handling of linear typing but renege on actually formulating this as part of their challenge they insist it is a future work here is the future
